%-------------------------
% CV in Latex
% Author : ingingx
%------------------------

\documentclass[9pt, a4paper]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://ingingX.github.io/}{\Large Yingpeng Ma}} & Email : \href{mailto:yingpengma@gmail.com}{yingpengma@gmail.com}\\
  \href{http://ingingX.github.io/}{http://ingingX.github.io/} & Mobile : +86-151-0848-2982 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Electronic Science and Technology of China (UESTC)}{Chengdu, China}
      {Bachelor of Communication Engineering}{Sep. 2015 - Jul. 2019}
      \resumeItemListStart
        \resumeItem{}
          {\textsl{GPA: 3.41/4.00 \qquad IELTS:7.0 \qquad GRE:319+3.0}}
        \resumeItem{}
          {\textsl{Relevant Module: Calculus, Linear Algebra, Probability and Mathematical Statistics, 
                  Software Technique, Digital Circuits, Signals and Systems, Mobile Communication Systems, 
                  Principle of Communications, Information Theory}}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Research Experience \& Intership}
  \resumeSubHeadingListStart

%-----CEEMD and LSSVM Prediction
    \resumeSubheading
      {Data Prediction Using CEEMD and LSSVM}{}
      {Practice Project}{Oct. 2019}
      \resumeItemListStart
        \resumeItem{Tensorflow}
          {TensorFlow is an open source software library for numerical computation using data flow graphs; primarily used for training deep learning models.}
        \resumeItem{Apache Beam}
          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines, as well as a set of language-specific SDKs for constructing pipelines and runners.}
      \resumeItemListEnd

%------MSK Simulation
    \resumeSubheading
      {Simulation of MSK System with Doppler Channel and Performance Improvement}{}
      {Practice Project}{Sep. 2019}
      \resumeItemListStart
        \resumeItem{Notifications}
          {Service for sending email, push and in-app notifications. Involved in features such as delivery time optimization, tracking, queuing and A/B testing. Built an internal app to run batch campaigns for marketing etc.}
        \resumeItem{Nostos}
          {Bulk data processing and injection service from Hadoop to Cassandra and provides a thin REST layer on top for serving offline computed data online.}
      \resumeItemListEnd

%------Pandas： HTML -> EXCEL
%---Selected
%    \resumeSubheading
%      {Converting HTML to EXCEL Content Using Python Pandas}{}
%      {Practice Project}{Sep. 2019}
%      \resumeItemListStart
%        \resumeItem{Portfolio Management}
%          {Created models for portfolio hedging,  portfolio optimization and price forecasting. Also creating a strategy backtesting engine used for simulating and backtesting strategies.}
%        \resumeItem{QuantDesk}
%          {Python backend for a web application used by hedge fund managers for portfolio management.}
%      \resumeItemListEnd

%------Undergraduate Thesis
    \resumeSubheading
      {Research of Transform Coding Based on Image Features}{UESTC, Chengdu}
      {Undergraduate Thesis, Supervised by Prof. Shuyuan Zhu}{Dec. 2018 - Jun. 2019}
      \resumeItemListStart
        \resumeItem{Research Assistant - Machine Learning}
          {Research on machine learning for portfolio hedging and replication algorithms. Modeling low-risk \& continuous-return strategies. Developed the python library QSTK.}
        \resumeItem{Teaching Assistant - Computational Investing}
          {The online course on Coursera, had more than 100,000 students enrolled. It was featured on the 11 Alive News and the Atlanta Journal Constitution. Involved in creating assignment, exams and conducting recitation sessions. Also taught the on-campus version of the course.}
      \resumeItemListEnd

%------Saliency: Bit-map & Bit-place Slicing
    \resumeSubheading
    {Image Saliency Detection with Bit-map and Bit-place Slicing}{UESTC, Chengdu}
    {Team Leader, Supervised by Prof. Bing Zeng, IEEE Fellow}{Sep. 2017 - Jun. 2019}
    \resumeItemListStart
      \resumeItem{Research Assistant - Machine Learning}
        {Research on machine learning for portfolio hedging and replication algorithms. Modeling low-risk \& continuous-return strategies. Developed the python library QSTK.}
      \resumeItem{Teaching Assistant - Computational Investing}
        {The online course on Coursera, had more than 100,000 students enrolled. It was featured on the 11 Alive News and the Atlanta Journal Constitution. Involved in creating assignment, exams and conducting recitation sessions. Also taught the on-campus version of the course.}
    \resumeItemListEnd

%------3.5mm image Trans
%---Selected
    \resumeSubheading
    {Image Transmission through a 3.5 mm Audio Cable}{UESTC, Chengdu}
    {Team Leader, Supervised by Prof. Xiaofeng Li}{Nov. 2017 - Dec. 2017}
    \resumeItemListStart
      \resumeItem{}
        {Established a system that transferred pictures between two computers(PCs) through a 3.5 mm audio cable (AUX).}
      \resumeItem{}
        {We designed mod \& demod system using DQPSK and coded the whole system on MATLAB and Simulink platforms.}
    \resumeItemListEnd

%------Datang Intership
    \resumeSubheading
    {Datang Telecom Technology}{Chengdu, China}
    {Intership}{Jul. 2017 - Sep. 2017}
    \resumeItemListStart
      \resumeItem{Engineer Assistant}
        {Initialized the base station settings and designed and simulated switching algorithm (Dijkstra) to reduce the network congestion.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Extra Curricular Achievement & Awards-----------------
\section{Extra Curricular Achievement \& Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{Contestant Assistant, China College Students Entrepreneurship Competition, 2016}
      {}
    \resumeSubItem{Exchange study in the National University of Singapore, 2016\\}
      {Completed courses in Engineering Management, won the Second Place with research on the business model of Uber.}
    \resumeSubItem{Outstanding Individual in Social Practices Scholarship of UESTC, 2016}
      {}
    \resumeSubItem{Third Place, Mathematical Competition of UESTC, 2016}
      {}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{ C++, Python, Java}
      \hfill
      \textbf{Software Platforms}{ MATLAB, Spyder3, VS}
    }

  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
